Can Auxiliary Indicators Improve COVID-19 Forecasting and Hotspot Prediction?

### 2021-06-17 forecast/paper/paper.tex
Temp commit so I can pull

Can axuiliary indicators improve COVID-19 forecasting and hotspot prediction
models?  Our answer, based on analyzing five auxiliary indicators from the  
COVIDcast API (defined using from medical insurance claims, internet-based
surveys, and Google search trends) is undoubtedbly ``yes''. However, there are 
levels of nuance to such an answer that must be explained.  None of the
indicators that we have investigated appear to be the ``silver bullet'' that 
one  might have hoped for, revolutionizing the tractability of the prediction 
problem, rendering it easy when it was once hard (in the absence of auxiliary 
information).  Rather, the gains in accuracy offered by the indicator models 
(over an autoregressive model based on past case rates along) appear to be
nontrivial, and consistent across modes of analysis, but modest.  In
forecasting, the indicator models appear to be most useful in periods in which 
case rates are flat or trending down, rather than periods in which case rates
are trending up (as one might hope to see, as the hypothetical benefit provided
by an idealized ``leading indicator'').

As mentioned previously, the indicator models could certainly benefit from a 
careful handling of location-specific effects (to account for spatial
heterogeneity in the search trends and claims-based indicators in particular),
as well as nowcasting techniques to estimate finalized indicator values before
using them as features (to account for backfill in the claims-based indicators
in particular).  Beyond this, it is certainly possible that more sophisticated 
models for forecasting or hotspot prediction would lead to different results,
and potentially even different insights.  Natural directions to explore include  
using interactions, using multiple indicators in tandem in a single model, and 
leveraging HRR demographics or mobility patterns.  That said, we are doubtful
that the ``topline'' conclusion would change--that auxiliary indicators can
provide a nontrivial, consistent, but modest improvement in forecasting and
hotspot prediction.

Furthermore, from our experience working on forecasting  TODO

>>>>

Can axuiliary indicators improve COVID-19 forecasting and hotspot prediction
models?  Our answer, based on analyzing five auxiliary indicators from the  
COVIDcast API (defined using from medical insurance claims, internet-based
surveys, and Google search trends) is undoubtedbly ``yes''. However, there are 
levels of nuance to such an answer that must be explained.  None of the
indicators that we have investigated appear to be the ``silver bullet'' that 
one might have hoped for, revolutionizing the tractability of the prediction 
problem, rendering it easy when it was once hard (in the absence of auxiliary 
information).  Rather, the gains in accuracy from the indicator models (over an
autoregressive model based only on past case rates) appear to be nontrivial, and
consistent across modes of analysis, but modest.  In forecasting, the indicator 
models appear to be most useful in periods in which case rates are flat or
trending down, rather than periods in which case rates are trending up (as one 
might hope to see is the benefit provided by a hypothetical ``leading
indicator'').

As mentioned previously, the indicator models could likely be improved by using 
location-specific effects, as well as using nowcasting techniques to estimate
finalized indicator values before using them as features (in order to account
for backfill in the claims-based signals in particular).  Beyond this, it is
certainly possible that more sophisticated models for forecasting or hotspot
prediction would lead to different results, and even different
insights. Natural directions to explore include using interactions, using
multiple indicators in a single model, and leveraging HRR demographics or
mobility patterns.  That said, we are doubtful that more sophisticated modeling
techniques would change the ``topline'' conclusion---that auxiliary indicators 
can provide nontrivial, consistent, but modest gains in forecasting and
hotspot prediction. Whether a more sophisticated model would be able to leverage
the indicators in such a way as to change some of the finer conclusions---e.g.,
by offering clear improvements in periods in which cases are trending up---is 
less clear to us.
